### 2020-03-16 paper/main.tex
edits

\addcontentsline{toc}{chapter}{Abstract}
\chapter{Acknowledgments}
[to do]
\tableofcontents
\listofillustrations

@@

@@

We analyzed our model on three radio signal datasets generated using Spatial Modulation. Spatial Modulation is a transmission technique that uses multiple antennae which maps a block of information bits to two units, a symbol chosen from a constellation diagram, and a unique transmit antenna number that is chosen from a set of transmit antennae \cite{mesleh_spatial_2008}. The method in which transmit antennae send and receive radio waves can be described through polarization. Two popular basis polarizations are horizontal linear, H, and vertical linear, V. Our datasets contain data horizontally transmitted and vertically received (HV), as well as data vertically transmitted and vertically received (VV).

@@

@@

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.6]{../media/stft.png}
   \end{center}
   \caption{Example of Short-Time Fourier Transform.}
   \label{fig:stft_example}
\end{figure}

@@

\subsection{Each Level of Decomposition as a Dataset}
Figure \ref{fig:multimodal_overview} depicts our model in which each level of decomposition is a unique dataset. This method and the resampling method both achieved similar results, so we chose to move forward with this method.
[make new figure]

@@

A Convolutional Neural Network is a type of deep neural network that can be applied to different domains such as computer vision or time series analysis. As seen in Figure X, it consists of an input and output layer as well as several hidden layers. A convolution is an operation between a vector of weights w against an input x \ref{}. It consists of taking the dot product between m and x in steps of a filter size defined by n.

@@

% create your own design
\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.3]{../media/nn_highlight.jpeg}
   \end{center}
   \caption{Example of a Convolutional Neural Network.}
   \label{fig:reinforcementAgent}
\end{figure}

@@

A standard LSTM unit is composed of a cell, an input gate, an output gate, and a forget gate. The cell remembers values over arbitrary time intervals, and the three gates regulate the flow of information into and out of the cell \ref{}.

LSTM networks are well-suited to classifying, processing, and making predictions based on time series data since there can be lags of unknown duration between significant events in a time series. LSTMs are developed to deal with the vanishing gradient problems that can are encountered when training traditional RNNs \ref{}.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/lstm_highlight.png}
   \end{center}
   \caption{Example of a LSTM unit.}
   \label{fig:reinforcementAgent}
\end{figure}

@@

% [multimodal]
Due to the superior performance and computationally tractable representation capability in multiple domains such as visual, audio, and text, deep neural networks have gained tremendous popularity in multimodal learning tasks \cite{kim_multimodal_2018}. Typically, domain-specific neural networks are used on different modalities to generate their representations, and the individual representations are merged or aggregated \ref{}. Finally, the prediction is made on top of aggregated representation, usually with another neural network to capture the interactions between models and learn complex function mapping between input and output.

@@

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.6]{../media/multimodal_overview.png}
   \end{center}
   \caption{Overview of our black-box model.}
   \label{fig:multimodal_overview}
\end{figure}

@@

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.6]{../media/mtf_q.png}
   \end{center}
   \caption{Example of QxQ quantile bin matrix used to calculate MTF.}
   \label{fig:mtf_q}
\end{figure}

@@

\section{Classification}
We apply MTF to our dataset and classify our images using a network similar to AlexNet, as shown in Figure \ref{fig:mtf_cnn_model}. We avoided using the CNN used in our black-box model in order to create a deeper and higher performing network. For this model, we define our input as images with dimensions 224x224, use a kernel size of 3x3, and apply max-pooling after every convolutional layer. We have five convolutional layers using 11, 256, 256, 384, and 384 filters, respectively, followed by two dense layers and a softmax layer.
\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=.7]{../media/2d_cnn.png}
   \end{center}
   \caption{CNN architecture for classifying images generated through MTF's.}
   \label{fig:mtf_cnn_model}
\end{figure}

@@

\section{Black-Box Model}
Our black-box model is constructed of three different architectures: 1 LSTM and 2 CNN’s that are all concatenated at their respective dense layer. The three features we use are the amplitude/phase of each level of decomposition for HV. We chose three because we wanted to increase the dimensionality of our data in the event that one had more descriptive features than the others.

@@

>>>>

\addcontentsline{toc}{chapter}{Abstract}
\chapter{Acknowledgments}

I want to thank Dr. Moon for his guidance and for allowing me to work on a project this extensive. I would also like to thank my friends and family for their continuous support throughout this thesis.

\tableofcontents
\listofillustrations

@@

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/overview_model.png}
   \end{center}
   \caption{Overview of our proposed hybrid model.}
   \label{fig:overview_model}
\end{figure}

@@

We analyzed our model on three radio signal datasets, which we will refer to as dataset A, B, and C throughout this thesis. These datasets were generated through Spatial Modulation which is a transmission technique that uses multiple antennae which maps a block of information bits to two units, a symbol chosen from a constellation diagram, and a unique transmit antenna number that is chosen from a set of transmit antennae \cite{mesleh_spatial_2008}. The method in which transmit antennae send and receive radio waves can be described through polarization. Two popular basis polarizations are horizontal linear, H, and vertical linear, V. Our datasets contain data horizontally transmitted and vertically received (HV), as well as data vertically transmitted and vertically received (VV).

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/dataset_info.png}
   \end{center}
   \caption{Size of each dataset.}
   \label{fig:stft_example}
\end{figure}

@@

The study of interpretable hybrid models has been worked on extensively in the past few years as deep learning has become increasingly popular. Scientists take different approaches as to what makes a hybrid model interpretable and apply it to different domains, such as computer vision or time series. For example, in \cite{wang_multilevel_2018}, they focus on creating a black-box model for the classification of time-series that outperforms similar architectures. However, their white-box model focuses on analyzing the importance of their model's layers. This helps users identify the importance of wavelet decomposition but not necessarily understand their dataset.

Additionally, other work we found tends to focus on non-time-series data or creating a general framework defining the trade-off between interpretability and black-box methods. For instance, \cite{wang_hybrid_2019} defines a set of rules to achieve a high level of classification with interpretability but does not give any competitive methods to achieve this.

In order to fill the gap for a high performing interpretable model for time-series classification, we propose our hybrid model, which focuses on extensibility and robustness. We achieve this through a combination of deep learning models for classification as well as a unique white-box method to explaining features within classes of a given dataset.

@@

\begin{figure}[h]
   \begin{center}
      \includegraphics[scale=0.6]{../media/stft.png}
   \end{center}
   \caption{Example of Short-Time Fourier Transform.}
   \label{fig:stft_example}
\end{figure}

@@

\subsection{Each Level of Decomposition as a Dataset}
Figure \ref{fig:multimodal_overview} depicts our model in which each level of decomposition is a unique dataset. This method and the resampling method both achieved similar results, so we chose to move forward with this method.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.35]{../media/wavelet_decomp.png}
   \end{center}
   \caption{Example of a wavelet decomposition network.}
   \label{fig:wavelet_decomp}
\end{figure}

@@

A Convolutional Neural Network is a type of deep neural network that can be applied to different domains such as computer vision or time series analysis. As seen in Figure X, it consists of an input and output layer as well as several hidden layers. A convolution is an operation between a vector of weights w against an input x \cite{yamashita_convolutional_2018}. It consists of taking the dot product between m and x in steps of a filter size defined by n.

@@

% create your own design
\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.3]{../media/nn_highlight.jpeg}
   \end{center}
   \caption{Example of a Convolutional Neural Network \cite{yamashita_convolutional_2018}.}
   \label{fig:cnn_example}
\end{figure}

@@

A standard LSTM unit is composed of a cell, an input gate, an output gate, and a forget gate. The cell remembers values over arbitrary time intervals, and the three gates regulate the flow of information into and out of the cell \cite{donahue_long-term_2016}.

LSTM networks are well-suited to classifying, processing, and making predictions based on time series data since there can be lags of unknown duration between significant events in a time series. LSTMs are developed to deal with the vanishing gradient problems that can are encountered when training traditional RNNs \cite{donahue_long-term_2016}.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/lstm_highlight.png}
   \end{center}
   \caption{Example of a LSTM unit \cite{donahue_long-term_2016}.}
   \label{fig:reinforcementAgent}
\end{figure}

@@

% [multimodal]
Due to the superior performance and computationally tractable representation capability in multiple domains such as visual, audio, and text, deep neural networks have gained tremendous popularity in multimodal learning tasks \cite{kim_multimodal_2018}. Typically, domain-specific neural networks are used on different modalities to generate their representations, and the individual representations are merged or aggregated \cite{kim_multimodal_2018}. Finally, the prediction is made on top of aggregated representation, usually with another neural network to capture the interactions between models and learn complex function mapping between input and output.

@@

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.65]{../media/multimodal_overview.png}
   \end{center}
   \caption{Overview of our black-box model.}
   \label{fig:multimodal_overview}
\end{figure}

@@

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.6]{../media/mtf_q.png}
   \end{center}
   \caption{Example of QxQ quantile bin matrix used to calculate MTF \cite{wang_encoding_nodate}.}
   \label{fig:mtf_q}
\end{figure}

@@

\section{Classification}
We apply MTF to our dataset and classify our images using a network similar to AlexNet, as shown in Figure \ref{fig:mtf_cnn_model}. We avoided using the CNN used in our black-box model in order to create a deeper and higher performing network. For this model, we define our input as images with dimensions 224x224, use a kernel size of 3x3, and apply max-pooling after every convolutional layer. We have five convolutional layers using 11, 256, 256, 384, and 384 filters, respectively, followed by two dense layers and a softmax layer.
\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=.7]{../media/2d_cnn.png}
   \end{center}
   \caption{CNN architecture for classifying images generated through MTF.}
   \label{fig:mtf_cnn_model}
\end{figure}

@@

\section{Black-Box Model}
Our black-box model is constructed of three different architectures: 1 LSTM and 2 CNN’s that are all concatenated at their respective dense layer (Figure \ref{fig:multimodal_overview}). The three features we use are the amplitude/phase of each level of decomposition for HV. We chose three because we wanted to increase the dimensionality of our data in the event that one had more descriptive features than the others.

Additionally, we tested our model using three levels of decomposition using the property VV as well as a combination of both VV and HV. We found no change in accuracy, therefore to limit the number of models we used, we only utilized the HV property.

@@

In order to generate images using MTF, we have to select three properties, and we chose P\textsubscript{1} as the radial value of HV's amplitude value, P\textsubscript{2} as the radial value of VV's amplitude value, and P\textsubscript{3} as the absolute squared distance between every P\textsubscript{1} and P\textsubscript{2}.

We then split those images using a randomized 70/30 split where 70\% of the data is our training set, and the other 30\% is our test set. We were able to achieve 60\% accuracy across all three of our datasets and show the features amongst the classes behave differently, as can be seen in Figure \ref{fig:whitebox_images}.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/whitebox_images.png}
   \end{center}
   \caption{Examples of images generated through MTF.}
   \label{fig:whitebox_images}
\end{figure}
